SUPPORTING INFORMATION \\ Determining sequence-dependent DNA oligonucleotide hybridization and dehybridization mechanisms using coarse-grained molecular simulation, Markov state models, and infrared spectroscopy

### 2021-05-20 SI.tex
final submission edits
Andy final edits prior to submission

% Fig. S2
\begin{figure}[ht!]
	\centering
    \includegraphics[width=0.8\textwidth]{FigS2.pdf}
    \caption{Convergence of the MSM implied time scales $t_i$ as a function of lag time $\tau$. Solid lines indicate maximum likelihood result while dashed lines show the Bayesian ensemble means superposed on shaded areas representing 95\% confidence intervals. The high simulation data volume used in our MSM construction means that the maximum likelihood and Bayesian ensemble means are in good agreement and confidence intervals are narrow. The implied time scales for all sequences converge at a lag time of $\tau$ = 1.2 ns (vertical line). The black solid curve marks equality of the implied time scale and lag time and delimits the shaded region wherein the implied time scales are shorter than the lag time and cannot be resolved.}
    \label{fig:SIFig2}
\end{figure}

@@

% Fig. S4
\begin{figure}[ht!]
	\centering
    \includegraphics[width=.75\textwidth]{FigS4.pdf}
    \caption{Exponential fits for both slow (dissociation) and fast (fraying) response for all four sequences during ``computational T-jump'' experiments. From 120 independent 1 $\mu$s simulations, we compiled the slow response data by recording the fraction of sequences with both central Watson-Crick base pairs intact as a function of time, and the fast response data as the fraction of sequences with both terminal Watson-Crick base pairs intact as a function of time. We define a Watson-Crick base pair to be intact if the two comlementary bases lie within a linear distance of 1.3 nm. We extracted our computational estimate of $k_d^\mathrm{fast}$ by fitting a decaying exponential to the fraction of bound A:T termini as a function of time $f_\mathrm{unfrayed}(t) = \exp(-k_d^\mathrm{fast}t)$. Similarly, we extracted our computational estimate of $k_d^\mathrm{slow}$ by fitting a decaying exponential to the fraction of hybridized sequences as a function of time $f_\mathrm{hybridized}(t) = \exp(-k_d^\mathrm{slow}t)$.}
    \label{fig:SIFig4}
\end{figure}

@@

The SantaLucia NN parameters are defined for a solution condition at neutral pH with a sodium concentration of 1M. We use the empirical salt correction developed by Owczarzy\citep{Owczarzy2008PredictingCations} to determine the NN parameters at the sodium concentration used for simulations in this work. The Owczarzy model assumes the effect of counter ions on DNA hybridization thermodynamics to be purely entropic,
\begin{equation}\label{SIe4}
\Delta S_{NN}^{\circ}(c_{Na^+}) = S_{NN}^{\circ}(1M) + \Delta H_{NN}^{\circ}[(4.29f_{GC}-3.95)\times 10^{-5} \ln{(c_{Na^+})}+ 9.4\times 10^{-6} (\ln{(c_{Na^+})})^2],
\end{equation} 
where $f_{GC}$ is the fractional G:C content of the duplex and $c_{Na^+}$ is the concentration of sodium counter ions measured in M.

>>>>

% Fig. S2
\begin{figure}[ht!]
	\centering
    \includegraphics[width=0.75\textwidth]{FigS2.pdf}
    \caption{Convergence of the MSM implied time scales $t_i$ as a function of lag time $\tau$. Solid lines indicate maximum likelihood result while dashed lines show the Bayesian ensemble means superposed on shaded areas representing 95\% confidence intervals. The high simulation data volume used in our MSM construction means that the maximum likelihood and Bayesian ensemble means are in good agreement and confidence intervals are narrow. The implied time scales for all sequences converge at a lag time of $\tau$ = 1.2 ns (vertical line). The black solid curve marks equality of the implied time scale and lag time and delimits the shaded region wherein the implied time scales are shorter than the lag time and cannot be resolved.}
    \label{fig:SIFig2}
\end{figure}

@@

% Fig. S4
\begin{figure}[ht!]
	\centering
    \includegraphics[width=.70\textwidth]{FigS4.pdf}
    \caption{Exponential fits for both slow (dissociation) and fast (fraying) response for all four sequences during ``computational T-jump'' experiments. From 120 independent 1 $\mu$s simulations, we compiled the slow response data by recording the fraction of sequences with both central Watson-Crick base pairs intact as a function of time, and the fast response data as the fraction of sequences with both terminal Watson-Crick base pairs intact as a function of time. We define a Watson-Crick base pair to be intact if the centers-of-mass of the two comlementary bases lie within a linear distance of 1.3 nm. We extracted our computational estimate of $k_d^\mathrm{fast}$ by fitting a decaying exponential to the fraction of bound A:T termini as a function of time $f_\mathrm{unfrayed}(t) = \exp(-k_d^\mathrm{fast}t)$. Similarly, we extracted our computational estimate of $k_d^\mathrm{slow}$ by fitting a decaying exponential to the fraction of hybridized sequences as a function of time $f_\mathrm{hybridized}(t) = \exp(-k_d^\mathrm{slow}t)$.}
    \label{fig:SIFig4}
\end{figure}

@@

The SantaLucia NN parameters are defined for a solution condition at neutral pH with a sodium concentration of 1M. We use the empirical salt correction developed by Owczarzy\citep{Owczarzy2008PredictingCations} to determine the NN parameters at the sodium concentration used for simulations in this work. The Owczarzy model assumes the effect of counter-ions on DNA hybridization thermodynamics to be purely entropic,
\begin{equation}\label{SIe4}
\Delta S_{NN}^{\circ}(c_{Na^+}) = S_{NN}^{\circ}(1M) + \Delta H_{NN}^{\circ}[(4.29f_{GC}-3.95)\times 10^{-5} \ln{(c_{Na^+})}+ 9.4\times 10^{-6} (\ln{(c_{Na^+})})^2],
\end{equation} 
where $f_{GC}$ is the fractional G:C content of the duplex and $c_{Na^+}$ is the concentration of sodium counter-ions measured in M.
